Hybrid Threads for the Parrot Virtual Machine

### 2012-04-17 Paper.tex
More about tests

\usepackage{wrapfig}
\AddBibFile{literature.bib}

@@

@@

>>>>

\usepackage{wrapfig}
\usepackage{listings}
\AddBibFile{literature.bib}

@@

\section{moretasks.pir}

moretasks.pir is an extended test where the main task creates 50000 child tasks. These tasks would poll a shared variable with pauses of 100ms. When the variable is set to 1, they schedule tasks on the main thread to write their number to a results array. When the results array contains the expected number of results the process is repeated. This test stresses reading and writing to shared data, allocation and garbage collection. This test proved to be valuable for finding all sorts of concurrency issues. The complete source code is available in appendix \ref{app:moretasks}.

\section{matrix\_part.winxed}

This test implements multiplication of a matrix by a vector using four threads. It is written in the \textit{Winxed} programming language. Winxed is a low level language with JavaScript like syntax and the possibility to include sections of PIR code verbatim making it possible to try experimental opcodes while writing more readable and concise code than with PIR alone. The complete source code is available in appendix \ref{app:matrix_part}.

\section{chameneos.pir}

Chameneos is a game useful for testing peer-to-peer cooperation of threads presented in \cite{Chameneos}. The complete source code is available in appendix \ref{app:chameneos_part}.

@@

There are several places with an implicit assumption that new threads may be only started from the main thread. Similarly only the main thread may schedule tasks on other threads. Sub threads may schedule tasks only on the main thread, not on other sub threads. These restrictions are not inherent in the implemented threading model but were introduced due to time constraints.

\appendix
\chapter{moretasks.pir}
\label{app:moretasks}

\begin{GenericCode}
.sub main :main
    .local pmc task, sayer, starter, number, interp, tasks, results
    .local int i, num_results, results_rem
    interp = getinterp
    sayer = get_global 'sayer'
init:
    starter = new ['Integer']
    i = 1
    starter = 0
    say "1..100"
    tasks = new ['ResizablePMCArray']
    results = new ['ResizablePMCArray']
start:
    number = new ['String']
    number = i
    task = new ['Task']
    push task, results
    push task, starter
    setattribute task, 'code', sayer
    setattribute task, 'data', number
    print "ok "
    say number
    push tasks, task
    schedule task
    inc i
    if i > 50000 goto run
    goto start
run:
    starter = 1
check_results:
    pass
    num_results = results
    results_rem = num_results % 1000
    if results_rem != 0 goto skip_say
    say num_results
skip_say:
    if num_results >= 50000 goto end
    goto check_results
end:
    goto init
.end

.sub sayer
    .param pmc name
    .local pmc interp, task, starter, results, result_sub, result_task
    .local int i
    interp = getinterp
    task = interp.'current_task'()
    starter    = pop task
    results    = pop task
    result_sub = get_global 'push_result'
start:
    if starter > 0 goto run
    sleep 0.1
    goto start
run:
    result_task = new ['Task']
    setattribute result_task, 'code', result_sub
    setattribute result_task, 'data', results
    push result_task, name
    interp.'schedule_proxied'(result_task, results)
.end

.sub push_result
    .param pmc results
    .local pmc interp, task, number
    interp = getinterp
    task = interp.'current_task'()
    number = pop task
    push results, number
.end
\end{GenericCode}

\chapter{matrix\_part.winxed}
\label{app:matrix_part}

\lstinputlisting{/home/nine/install/parrot/examples/threads/matrix_part.winxed}

\chapter{chameneos.pir}
\label{app:chameneos_part}

\lstinputlisting{/home/nine/install/parrot/examples/threads/chameneos.pir}
